---
title: "Summary statistics"
output: html_document
date: "2022-07-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

setwd('C:/Users/Michelle Edwards/Documents/MD Hackathon')
```

## R Markdown

First we need to read in the dataset:

```{r read in files}
df <- read.csv('Bike_Rack_Use_By_Stop_By_Fiscal_Week.csv')
```

## Some plots

Let's try a histogram of the totals across all the weeks.

```{r hist1}
ggplot(df) +
  geom_histogram(aes(x = Total), binwidth = 500) +
  theme_bw()
```

I think the datapoint with > 30000 uses is a total of the others. We should check this:

```{r check large datapoint}
mystery_row <- df[df$Total > 30000,]

df_updated <- df[df$Total <= 30000,]
# numeric columns are 3 to 65
colsums <- colSums(df_updated[,3:65])

together <- rbind(mystery_row[,3:65], colsums)

# check if they are equal everywhere
sum(mystery_row[,3:65] - colsums)

which((mystery_row[,3:65] - colsums)>0)

sum(df_updated[,62])
mystery_row[,62]
```

They are only different in one place. We will assume this is an error and proceed with removing the total row:
```{r hist2}
ggplot(df_updated) +
  geom_histogram(aes(x = Total), binwidth = 1) +
  ggtitle("Total number of stops") +
  theme_bw()

ggplot(df_updated[df_updated$Total < 100,]) +
  geom_histogram(aes(x = Total), binwidth = 1) +
  ggtitle("Total number of stops (where total < 100)") +
  theme_bw()
```

Summary stats of total stops over all weeks
```{r summary stats 1}

summary(df_updated$Total)

```


Summary stats of total stops over each week 
```{r summary stats 2}

summary(t(mystery_row[,3:65]))

```


Summary stats of stops at racks for each week
```{r summary stats 3}

summary(df_updated)

```

Busiest rack?
```{r busiest rack}

df_updated[which.max(df_updated$Total),]$Stop.Name

```


Busiest week? **Not sure how to convert this to a week**
```{r busiest week}

which.max(mystery_row)

```


Busiest rack on the busiest week?
```{r busiest week rack}

df_updated[which.max(df_updated[,which.max(mystery_row)]),]$Stop.Name

```